Data Analysis

### 2022-07-26 04.manuscript_scopus.Rmd
updated manuscript draft

The introduction will go here. Here's an outline:

- Big Team Science
  - one off papers 
  - collaborative teams 
- Credibility revolution
- WEIRD 
- ... more tbd, brain isn't braining

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

**_Employment_**. We will summarize the general employment categories of individuals at the time of publication, along with a summary for change over time.

**_Education_**. We will summarize the general education categories of individuals at the time of publication, along with a summary for change over time.

@@

**_Publication Metrics_**. We will report descriptive statistics on the total number of publications, i10 index, and h-index for individuals overall. Next, we will use the same analyses described in the career length section to analyze trends over time. An increasing slope over time indicates that individuals who are publishing more are more represented in big-team science over time (i.e., increasing numbers of scholars with higher publication rates), while a negative slope indicates more researchers with less publications. A positive slope for variance indicates increasing variance over time (i.e., more diversity in the individual publication rates), while a negative slope would indicate less diversity in researchers over time. While publication rates do not represent value as a researcher, they are often used in hiring and promotion decisions, and we will use this variable as a proxy to gauge the diversity in scholars represented in big teams.

@@

Given the expected small sample sizes of these contingency tables (i.e., the largest could be *n* = 22 if all author information is available), we will group together titles based on time period using pre-2020, 2020, and post-2020 to show change over time. The choice of these groupings is based on the number of articles avaliable within these time brackets. For each grouping, we will calculate the effect size of the differences in frequencies comparing first authors to all other authors. Since this data is categorical, we will use Cramer's V to represent the effect size. If the effect size includes zero in it's confidence interval, this result will imply that first and all other authors represent the same pattern of UN Sub-Region diversity. Any confidence interval that does include zero represents a difference in diversity. We will report these values and discuss what regions of the world are represented when effect sizes indicate a different from zero using standardized residuals.

>>>>

# Significance

science collaboration overall 
  - what is collaboration
  - is it increasing 
  - globalization should help

rise of big team science because the need for resources, replication, reproducibility, generalization  
  - physics
  - biology 
  - psychology

metascience
  - most research is on lessons learned, why bts is useful
  - little research on who/fields has done bts
  - has the globalization of science actually impacted people other than NA and Europe

Collaboration in scientific endeavors involves multiple researchers at multiple institutions to communicate and work together to advance knowledge in their chosen field. While collaboration is not new in science, the current interest of "big team science" is increasing. We define big team science as at least ten authors with ten different institutional affiliations. The globalization of science has allowed researchers across the world to contribute to research projects, but little research has examined *who* participates in big team science projects.

idea of BTS is not new, but interest is new, and globalization allows us to do BTS with projects such as PSA/CERN/Reproducibility projects. But we don't know if this uptick in large scale projects has diversified the *people* involved in BTS. Is this increasing inclusivity? At what level of career are people doing BTS? Is that changing over time? And how is that including new and varied researchers outside NA and Europe? Are we including people in positions that may impact their career? WERID thing is innovative

    Significance: Describe how the project addresses an important problem or a critical barrier to progress in the field and how it can advance knowledge in the ICSR Research Themes.

We specifically expect to examine ICSR's Research Themes of inclusivity, research careers, and research globalization. As we examine these themes, it will a bring new knowledge of how big team science projects impact each theme and field of study.

# Potential Outlets

We will aim for high impact broad scope journals such as *Science*, *Nature* or *Nature Human Behaviour*. Other journals would include review publications within psychology to compare the social sciences to other sciences: *Perspectives in Psychological Science*, *Psychological Bulletin*, *Psychological Review*, or *Current Directions in Psychological Science*.

# Approach

    Approach: Please describe:
        An explicit research question or hypothesis you plan to test, and specific aims/objective related to that question.
        The project’s overall strategy and planned methodology.
        How the proposed project will make use of one or more of the available ICSR Lab datasets.
        Any especially innovative or novel aspect of the proposed project.

@@

- definition for big team size: 10 authors + at least 10 different institutions
- we will use all categories but break into the big four: https://service.elsevier.com/app/answers/detail/a_id/14882/supporthub/scopus/~/what-are-the-most-frequent-subject-area-categories-and-classifications-used-in/ 
- we would get everything from df_ani 
- only use 1970 and forward

@@

journal information we could include:
  - total number of articles overall 
  - number of distinct journals in each of the four areas 
  - JIF df_sources, snip
  - https://liu.cwp.libguides.com/c.php?g=45770&p=4417804

@@

- keywords are easier now - could use the ASJC smaller subfield areas to create a list 
- https://service.elsevier.com/app/answers/detail/a_id/15181/supporthub/scopus/
- table of all the codes

@@

- calculate the min to max
- average authors 
- SD authors

@@

- here we would pull all author ids and then grab all their papers - grab from the whole dataset not just 1970

@@

- year from first publication should be what we would do

@@

- can't get this part really - we could get institution from publication and country from publication

@@

- we can get the degrees from the author table

@@

- publication type:

The classification of the publication, which may be: ab Abstract Report, ar Article, ip Article in Press, bk Book, bz Business Article, ch Book Chapter, cp Conference Paper, cr Conference Review, dp Data paper, ed Editorial, er Erratum, le Letter, no Note, pp Preprint, pr Press Release, rp Report, re Review, sh Survey, tb Retracted.

- just make a graph of the options

@@

- for each author:
  - total number of publications
  - h index
  - i 10 index

@@

- so we cant do MLM 
- for each paper we could calculate an average career length, then run the regression 
- then calculate the standard deviation and do the same analysis as described

**_Employment_**. We will summarize the general employment categories of individuals at the time of publication, along with a summary for change over time. 
**_Education_**. We will summarize the general education categories of individuals at the time of publication, along with a summary for change over time.

@@

**_Publication Metrics_**. We will report descriptive statistics on the total number of publications, i10 index, and h-index for individuals overall. Next, we will use the same analyses described in the career length section to analyze trends over time. An increasing slope over time indicates that individuals who are publishing more are more represented in big-team science over time (i.e., increasing numbers of scholars with higher publication rates), while a negative slope indicates more researchers with less publications. A positive slope for variance indicates increasing variance over time (i.e., more diversity in the individual publication rates), while a negative slope would indicate less diversity in researchers over time. While publication rates do not represent value as a researcher, they are often used in hiring and promotion decisions, and we will use this variable as a proxy to gauge the diversity in scholars represented in big teams. 
same idea average down by paper for mean and standard deviation

@@

- may not need to do this random sample thing if we have large enough datasets? 
- pool them together and then compare? 
- maybe group them in the sizes we are interested in, then convert to proportions
- average those proportions ? plot comparisons of the proportions and confidence intervals for each group

Given the expected small sample sizes of these contingency tables (i.e., the largest could be *n* = 22 if all author information is available), we will group together titles based on time period using pre-2020, 2020, and post-2020 to show change over time. The choice of these groupings is based on the number of articles available within these time brackets. For each grouping, we will calculate the effect size of the differences in frequencies comparing first authors to all other authors. Since this data is categorical, we will use Cramer's V to represent the effect size. If the effect size includes zero in it's confidence interval, this result will imply that first and all other authors represent the same pattern of UN Sub-Region diversity. Any confidence interval that does include zero represents a difference in diversity. We will report these values and discuss what regions of the world are represented when effect sizes indicate a different from zero using standardized residuals.
